A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex
adding to abstract
fix abstarct

\documentclass[%
reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
%rmp,
prstab,
%prstper,
%floatfix,
]{revtex4-1}

@@

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame a fast 
  and scalable software framework is required.
In this paper, we present the implementation of such a general-purpose
  framework for simulation-based multi-objective optimization methods that
  allows the automatic investigation of optimal sets of machine parameters.
The implementation is based on a master/slave paradigm, employing several
  masters that govern a set of slaves executing simulations and performing
  optimization tasks.
Using evolutionary algorithms and \textsc{OPAL}~simulations as optimizer and
  forward solver in our framework, validation experiments and first
  results of multi-objective optimization problems in the domain of beam
  dynamics is presented.

>>>>

\documentclass[%
preprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
preprint,
linenumbers,
%showpacs,preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
amsmath,amssymb,
aps,
%pra,
%prb,
%rmp,
prstab,
%prstper,
%floatfix,
]{revtex4-1}

@@

\begin{abstract}
Particle accelerators are invaluable tools for research in the basic and
  applied sciences, in fields such as materials science, chemistry,
  the biosciences, particle physics, nuclear physics and medicine.
The design, commissioning, and operation of accelerator facilities is a
  non-trivial task, due to the large number of control parameters and the
  complex interplay of several conflicting design goals.
We propose to tackle this problem by means of multi-objective optimization
  algorithms which also facilitate a parallel deployment.
In order to compute solutions in a meaningful time frame a fast 
  and scalable software framework is required.
In this paper, we present the implementation of such a general-purpose
  framework for simulation-based multi-objective optimization methods that
  allows the automatic investigation of optimal sets of machine parameters.
The implementation is based on a master/slave paradigm, employing several
  masters that govern a set of slaves executing simulations and performing
  optimization tasks.
Using evolutionary algorithms as the optimizer and \textsc{OPAL} as the 
  forward solver, validation experiments and 
 results of multi-objective optimization problems in the domain of beam
  dynamics are presented. The high charge beam line at the Argonne Wakefield 
  Accelerator Facility was used as the beam dynamics model. The 3D beam size, 
  transverse momentum, and energy spread were optimized.
